Psychological Needs During Intergroup Contact

### 2022-01-05 Methods-and-Results.Rmd
general tbl escape fix

#mdlTblGeneralLong <- 
  rbind(mdlTblGeneralLm %>%
                             filter(
                               coef %in% c(
                                 "(Intercept)",
                                 "SumContactNL",
                                 "AvQuality",
                                 "SumContactNL:AvQuality",
                                 "R2_R2_adjusted"
                               )
                             ),
                           mdlTblGeneralLmer %>%
                             filter(
                               coef %in% c(
                                 "(Intercept)",
                                 "OutgroupInteraction",
                                 "NonOutgroupInteraction",
                                 "R2Marg_R2Cond"
                               )
                             )) %>%
    replace(is.na(.), "") %>%
  kbl(
    .,
    caption = "Intergroup General",
    #format = "latex",
    linesep = "",
    booktabs = TRUE,
    col.names = c("", rep(c("$B$", "Effect Size"), (ncol(.)-1)/2)),
    align = c("l", rep("c", ncol(.) - 1)),
    escape = FALSE,
    digits = 3
  )  %>%
  kable_classic() %>%
  add_header_above(
    .,
    c(
      "",
      "Study 1" = 2,
      "Study 2" = 2,
      "Study 3" = 2
    )
  ) %>%
  pack_rows("Between Participant [aggregated linear regression] (ES = $\\eta_{partial}$)", 1, 5) %>%
  pack_rows("Within Participants [multilevel linear regression] (ES = $Beta$)", 6, 9) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  kableExtra::landscape() %>%
  save_kable("Tables/mdlContactGeneralLong.tex")
```

>>>>

#mdlTblGeneralLong <- 
  rbind(mdlTblGeneralLm %>%
                             filter(
                               coef %in% c(
                                 "(Intercept)",
                                 "SumContactNL",
                                 "AvQuality",
                                 "SumContactNL:AvQuality",
                                 "R2_R2_adjusted"
                               )
                             ),
                           mdlTblGeneralLmer %>%
                             filter(
                               coef %in% c(
                                 "(Intercept)",
                                 "OutgroupInteraction",
                                 "NonOutgroupInteraction",
                                 "R2Marg_R2Cond"
                               )
                             )) %>%
    replace(is.na(.), "") %>%
  kbl(
    .,
    caption = "Intergroup General",
    #format = "latex",
    linesep = "",
    booktabs = TRUE,
    col.names = c("", rep(c("$B$", "Effect Size"), (ncol(.)-1)/2)),
    align = c("l", rep("c", ncol(.) - 1)),
    escape = FALSE,
    digits = 3
  )  %>%
  kable_classic() %>%
  add_header_above(
    .,
    c(
      "",
      "Study 1" = 2,
      "Study 2" = 2,
      "Study 3" = 2
    )
  ) %>%
  pack_rows("Between Participant [aggregated linear regression] (ES = $\\eta_{partial}$)", 1, 5, escape = FALSE) %>%
  pack_rows("Within Participants [multilevel linear regression] (ES = $Beta$)", 6, 9, escape = FALSE) %>%
  kable_styling(latex_options = "scale_down") %>%
  gsub("\\begin{table}", "\\begin{table}\n\\begin{minipage}[t][\\textheight][t]{\\textwidth}", ., fixed = TRUE) %>% # fix table position
  gsub("\\end{table}", "\\end{minipage}\n\\end{table}", ., fixed = TRUE) %>% # fix table position
  kableExtra::landscape() %>%
  save_kable("Tables/mdlContactGeneralLong.tex")
```
